The population of long-period exoplanets --- \\ Fully-automated discovery \& characterization of long-period transiting exoplanet candidates in the \kepler\ archive \vspace{-3\baselineskip}

### 2016-06-29 document/ms.tex
captions

\begin{figure}~\\
\begin{center}
\includegraphics{figures/targets.pdf}
\end{center}
\caption{%
Blah.
\dfmfiglabel{targets}}~\\
\end{figure}

@@

\begin{figure*}[p]~\\
\begin{center}
\include{lcfig}
\end{center}
\caption{%
\dfmfiglabel{lightcurves}}
\end{figure*}

\begin{figure*}~\\
\begin{center}
\includegraphics{figures/full_sample_plus_cands.pdf}
\end{center}
\caption{%
Blah.
\dfmfiglabel{full-sample}}~\\
\end{figure*}

\begin{deluxetable}{cccccl}
\tabletypesize{\footnotesize}
\tablecaption{caption\label{tab:table}}
\include{paramtab}
% \tablenotetext{a}{Adjusted for inflation}
% \tablenotetext{b}{Accounts for the change from page charges to digital quanta in April, 2011}
% \tablecomments{Note that {\tt \string \colnumbers} does not work with the
% vertical line alignment token. If you want vertical lines in the headers you
% can not use this command at this time.}
\end{deluxetable}

>>>>

\begin{figure}~\\
\begin{center}
\includegraphics{figures/targets.pdf}
\end{center}
\caption{%
The distribution of stellar parameters for \kepler\ targets selected for this
search (orange) compared to the distribution of the full \kepler\ target
catalog (black).
\dfmfiglabel{targets}}~\\
\end{figure}

@@

\subsection{Catalog of candidates}

\begin{deluxetable}{cccccl}
\tabletypesize{\footnotesize}
\tablecaption{The inferred parameters for the long-period transiting exoplanet
candidates
\label{tab:table}}
\include{paramtab}
\tablenotetext{\dagger}{Candidate has two observed transits.}
\tablenotetext{a}{Included in the \citet{Wang:2015} catalog.}
\tablenotetext{b}{Included in the \citet{Uehara:2016} catalog.}
\end{deluxetable}

\begin{figure*}[p]~\\
\begin{center}
\include{lcfig}
\end{center}
\caption{%
Sections of PDC light curve centered on each candidate (black) with the
posterior-median transit model over-plotted (orange).
Candidates with two transits are folded on the posterior-median period.
\dfmfiglabel{light-curves}}
\end{figure*}

\begin{figure*}~\\
\begin{center}
\includegraphics{figures/full_sample_plus_cands.pdf}
\end{center}
\caption{%
The catalog of long-period transiting exoplanet candidates (green) compared to
the \kepler\ candidates (blue) and confirmed planets (black), and the Solar
System (orange).
The vertical dashed line indicates the full lifetime of the \kepler\ Mission;
planets with orbital periods longer than this will show at most one transit.
The vertical solid line shows the absolute maximum period accessible to
transit searches that require at least three transits.
\dfmfiglabel{full-sample}}~\\
\end{figure*}
